R Notebook

### 2021-09-02 notebooks/metric_performance_tables.rmd

metric_levels <- c("emb", "levyeuc", "dot", "pprjsd", "svdcos", "levycos", "geo",
                   "lapcos", "pprcos", "levydot")

metric_labels <- c("Embedding cosine", "Factorized euclidean", "Embedding dot", "PPR JSD", 
                   "SVD cosine", "Factorized cosine", "Geographic", "Laplacian cosine", "PPR cosine", "Factorized dot")

@@

r2.hux <- as_hux(r2.tab) %>%
  set_contents(1, 2:10, rep(c("Global", "Domestic", "International"), 3)) %>%
  insert_row("", "All", "", "", "Mobile only", "", "", "Raw freq", "", "", after = 0) %>% 
  merge_cells(1, 2:4) %>% 
  merge_cells(1, 5:7) %>% 
  merge_cells(1, 8:10) %>%
  set_tb_padding(1, everywhere, 0) %>% 
  set_bold(1, everywhere) %>%
  map_align(by_cols(c("left", rep("right", 9)))) %>%
  set_align(1, everywhere, "center") %>% 
  #map_align(row = 1, by_cols(rep("center", 10))) %>%
  set_header_rows(1:2, TRUE) %>% 
  set_header_cols(1, TRUE) %>% 
  style_headers(bold = TRUE) %>%
  set_right_border(1:12, 1, value = 0.5) %>%
  set_right_border(1:12, 4, value = 0.5) %>%
  set_right_border(1:12, 7, value = 0.5) %>%
  set_bottom_border(2, 1:10, value = 0.5)

@@

rmse.hux <- as_hux(rmse.tab) %>%
  set_contents(1, 2:10, rep(c("Global", "Domestic", "International"), 3)) %>%
  insert_row("", "All", "", "", "Mobile only", "", "", "Raw freq", "", "", after = 0) %>% 
  merge_cells(1, 2:4) %>% 
  merge_cells(1, 5:7) %>% 
  merge_cells(1, 8:10) %>%
  set_tb_padding(1, everywhere, 0) %>% 
  set_bold(1, everywhere) %>%
  map_align(by_cols(c("left", rep("right", 9)))) %>%
  set_align(1, everywhere, "center") %>% 
  #map_align(row = 1, by_cols(rep("center", 10))) %>%
  set_header_rows(1:2, TRUE) %>% 
  set_header_cols(1, TRUE) %>% 
  style_headers(bold = TRUE) %>%
  set_right_border(1:12, 1, value = 0.5) %>%
  set_right_border(1:12, 4, value = 0.5) %>%
  set_right_border(1:12, 7, value = 0.5) %>%
  set_bottom_border(2, 1:10, value = 0.5)

>>>>

metric_levels <- c("emb", "levyeuc", "dot", "pprjsd", "svdcos", "levycos", "geo",
                   "lapcos", "pprcos", "levydot", "gravsvd", "gravmds")

metric_labels <- c("Embedding cosine", "Levy's euclidean", "Embedding dot", "PPR JSD", 
                   "SVD cosine", "Levy's cosine", "Geographic", "Laplacian cosine", "PPR cosine", "Levy's dot", "Gravity SVD cosine", "Gravity MDS euclidean")

@@

r2.hux <- as_hux(r2.tab) %>%
  set_contents(1, 2:10, rep(c("Global", "Domestic", "International"), 3)) %>%
  insert_row("", "All", "", "", "Mobile only", "", "", "Raw freq", "", "", after = 0) %>% 
  merge_cells(1, 2:4) %>% 
  merge_cells(1, 5:7) %>% 
  merge_cells(1, 8:10) %>%
  set_tb_padding(1, everywhere, 0) %>% 
  set_bold(1, everywhere) %>%
  map_align(by_cols(c("left", rep("right", 9)))) %>%
  set_align(1, everywhere, "center") %>% 
  #map_align(row = 1, by_cols(rep("center", 10))) %>%
  set_header_rows(1:2, TRUE) %>% 
  set_header_cols(1, TRUE) %>% 
  style_headers(bold = TRUE) %>%
  set_right_border(1:14, 1, value = 0.5) %>%
  set_right_border(1:14, 4, value = 0.5) %>%
  set_right_border(1:14, 7, value = 0.5) %>%
  set_bottom_border(2, 1:10, value = 0.5)

@@

rmse.hux <- as_hux(rmse.tab) %>%
  set_contents(1, 2:10, rep(c("Global", "Domestic", "International"), 3)) %>%
  insert_row("", "All", "", "", "Mobile only", "", "", "Raw freq", "", "", after = 0) %>% 
  merge_cells(1, 2:4) %>% 
  merge_cells(1, 5:7) %>% 
  merge_cells(1, 8:10) %>%
  set_tb_padding(1, everywhere, 0) %>% 
  set_bold(1, everywhere) %>%
  map_align(by_cols(c("left", rep("right", 9)))) %>%
  set_align(1, everywhere, "center") %>% 
  #map_align(row = 1, by_cols(rep("center", 10))) %>%
  set_header_rows(1:2, TRUE) %>% 
  set_header_cols(1, TRUE) %>% 
  style_headers(bold = TRUE) %>%
  set_right_border(1:14, 1, value = 0.5) %>%
  set_right_border(1:14, 4, value = 0.5) %>%
  set_right_border(1:14, 7, value = 0.5) %>%
  set_bottom_border(2, 1:10, value = 0.5)
